Sound Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
review Overview of the Synthesis Process using DSVerifier

%------------------------------------
\subsection{Synthesis Process using DSVerifier}
\label{verification-flow}
%------------------------------------

@@

The full synthesis process is illustrated in Fig.~\ref{DSVerifier_process};
a detailed description of DSVerifier tool can be found in~\cite{IsmailBCFF15}.
Steps $1$ to $5$ are performed by the user/synthesiser and
Steps A to D are automatically performed by DSVerifier.
%, which accepts the
%digital controller transfer functions together with the plant model.  For
%any digital controller, implementation details should be provided ({\it
%e.g.}, number of bits, realization, and sample time).

@@

Given a model for a plant for which to synthesize a controller,
provided in an ANSI-C code input file (Steps 1-5), DSVerifier constructs a
non-deterministic model to represent the plant family (Step A), and a transfer
function $f$ represented by Eq.~\ref{FWL_tf} (step B) to calculate the parameters
of the controller to be synthesized (step C).  Finally DSVerifier builds an
intermediate ANSI-C code for the digital system implementation, which is used as
input for the controller synthesiser (Step D).

This intermediate ANSI-C code model contains a specification $\phi$ for the
verification properties ({\it i.e.}, robust stability) and is provided to
CBMC's~\cite{ClarkeKL04} integrated Counterexample-Guided Inductive Synthesis
(CEGIS) module, where the controller is marked as input variable to synthesize.
The properties specified in the ANSI-C code model can only be satisfied if CEGIS
synthesizes controller coefficients satisfying $\phi$. CEGIS employs an iterative,
counterexample-guided refinement process which is explained in detail in
section~\ref{synthesiser-general}. A successful synthesis result is reported if
CEGIS generates a controller which is safe with respect to $\phi$.  In particular,
the ANSI-C code model guarantees that a synthesized solution is complete
and sound with respect to stability property $\phi$, since it does not depend on
system inputs and outputs.  In the case of stability, the specification $\phi$
consists in a number of assumptions on the polynomial coefficients, following
Jury's Criteria, as well as the restrictions set in the representation of these
coefficients by the function $f$ (cf.~Eq.~\eqref{FWL_tf}).

%In Step A, DSVerifier constructs a non-deterministic model to represent the
%plant family $\mathfrak{G}$ using $g_0$ and $\Delta{g}\%$, which are
%provided in Step $1$.  DSVerifier then formulates $\mathit{FWL}[\cdot]$ in
%Step B using implementation details provided from Steps $2$ and $3$, and
%then computes $\mathit{FWL}[c_0]$ in Step C.  Thus, DSVerifier builds an
%intermediate ANSI-C code for the digital system implementation, which is
%used as input for the model-checker, as pointed in Step D.

>>>>

%------------------------------------
\subsection{Overview of the Synthesis Process using DSVerifier}
\label{verification-flow}
%------------------------------------

@@

An overview of the synthesis process is illustrated in Fig.~\ref{DSVerifier_process};
a detailed description of DSVerifier tool can be found in~\cite{IsmailBCFF15}.
Steps $1$ to $5$ are performed by the user/synthesiser and
Steps A to D are automatically performed by DSVerifier.
%, which accepts the
%digital controller transfer functions together with the plant model.  For
%any digital controller, implementation details should be provided ({\it
%e.g.}, number of bits, realization, and sample time).

@@

Given a model for a plant for which to synthesize a controller,
provided in an ANSI-C code input file (Steps 1-5), DSVerifier constructs a
non-deterministic model to represent the plant family (Step A), and formulates a 
function (step B) using implementation details provided from Steps $2$ and $3$ 
to calculate the parameters of the controller to be synthesized (step C).  
Finally DSVerifier builds an intermediate ANSI-C code for the digital system 
implementation, which is used as input for the controller synthesiser (Step D).

This intermediate ANSI-C code model contains a specification $\phi$ for the
verification properties ({\it i.e.}, robust stability) and is provided to
CBMC's~\cite{ClarkeKL04} integrated Counterexample-Guided Inductive Synthesis
(CEGIS) module, where the controller is marked as input variable to synthesize.
The properties specified in the ANSI-C code model can only be satisfied if CEGIS
synthesizes controller coefficients satisfying $\phi$. CEGIS employs an iterative,
counterexample-guided refinement process which is explained in detail in
section~\ref{synthesiser-general}. A successful synthesis result is reported if
CEGIS generates a controller which is safe with respect to $\phi$.  In particular,
the ANSI-C code model guarantees that a synthesized solution is complete
and sound with respect to stability property $\phi$, since it does not depend on
system inputs and outputs.  In the case of stability, the specification $\phi$
consists in a number of assumptions on the polynomial coefficients, following
Jury's Criteria, as well as the restrictions set in the representation of these
coefficients.

% by the function $f$ (cf.~Eq.~\eqref{FWL_tf})
%In Step A, DSVerifier constructs a non-deterministic model to represent the
%plant family $\mathfrak{G}$ using $g_0$ and $\Delta{g}\%$, which are
%provided in Step $1$.  DSVerifier then formulates $\mathit{FWL}[\cdot]$ in
%Step B using implementation details provided from Steps $2$ and $3$, and
%then computes $\mathit{FWL}[c_0]$ in Step C.  Thus, DSVerifier builds an
%intermediate ANSI-C code for the digital system implementation, which is
%used as input for the model-checker, as pointed in Step D.
